Incentivizing Exploration with Unbiased History

### 2018-11-02 llevel-overview.tex
editing...

This motivates the following interlacing connection structure between levels. For each level in the info-graph, there are  $\NG^2$ groups for some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,...,L\}$ and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of agents in group $G_{l-1,v,w}$ (and by transitivity all agents in levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a graphical view (as space limit, we only show 3 levels and 4 groups in each level).

This connecting structure has the following nice properties: \\
\OMIT{(i) The number of groups does not grow with $L$ and stays as $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
(i) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ with red circles in the figure ) as a set of groups indexed by $l-1$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(ii) For each set of groups in level $l-1$, agents in level $l$ see
the history of agents in one of these groups. Therefore, for each arm
$a$, we just need one set of groups in level $l-1$ to get ``lucky''
and then all agents in level $l$ will see enough pulls of arm $a$.

>>>>

This motivates the following interlacing connection structure between
levels. For each level in the info-graph, there are $\NG^2$ groups for
some $\NG = \Theta(\log(T))$. The groups in the $l$-th level are
labeled as $G_{l,u,v}$ for $u,v\in[\NG]$. For any $l \in \{2,...,L\}$
and $u,v,w\in [\NG]$, agents in group $G_{l,u,v}$ see the history of
agents in group $G_{l-1,v,w}$ (and by transitivity all agents in
levels below $l-1$). See Figure \ref{fig:llevel-connecting} for a
visualization of simple case with $\sigma = 2$).

This connecting structure has the following nice properties: \\
\OMIT{(i) The number of groups does not grow with $L$ and stays as
  $\NG^2 = \Theta(\log^2(T))$ in each level. Having these groups only
  incurs a $\Theta(\log^2(T))$ multiplicative factor to the regret.\\}
(i) Consider groups $G_{l-1,1,v},G_{l-1,2,v},...,G_{l-1,\NG,v}$ (e.g. $G_{l-1,1,1}$ and $G_{l-1,2,1}$ circled in the Figure \ref{fig:llevel-connecting}) as a set of groups indexed by $l-1$ and $v$. The agents in a set of groups see the same history. They get ``lucky'' for some arm at the same time.\\
(ii) For each set of groups in level $l-1$, agents in level $l$ see
the history of agents in one of these groups. Therefore, for each arm
$a$, we just need one set of groups in level $l-1$ to get ``lucky''
and then all agents in level $l$ will see enough pulls of arm $a$.
